More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-09-20 2016-Weak-FH-Bisim/WeakBisim.tex
use \True et \Id #8

Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
$\mathcal{S}_2$ constrained by a predicate
More precisely, for any pair $(s,t)$, there is a 
   single
      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
      if $\Pred_{s,t}$       is 
      true, i.e. the states are related when the variables in $s$ and $t$ verify the 
      predicate $\Pred_{s,t}$.
 FH-bisimulation is defined formally: 
 \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}

@@

     $  OT_2  = \openrule{
      \emptyset; Pred=true;  \\ Post=\{m_1\_m:=s_1\_m, m_1\_b:=s_1\_sb, s_2\_sb:=s_1\_sb\}
                      }
    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(s_1\_m, s_1\_b)}} \ostate{s_2,m_1,m_0,r_0}}
    $

@@

\subsection{Bisimulation for open pNets and Composability}
\label{section:bisimulation-PN}
As  our symbolic operational semantics provides an open automaton, we can apply the notion of
	strong (symbolic) bisimulation on automata to open pNet s:
\begin{definition}[FH-bisimulation for open pNets]\label{def:bisim-pnets}
Two pNets are FH-bisimilar if there exist a relation between their associated 
automata that is an FH-bisimulation and their initial states are in the relation, i.e. 
the predicate associated to the relation between the initial states is true.
\end{definition}
We can now prove that pNet composition  preserves
FH-bisimulation. More precisely, one can define two preservation
properties, namely 1) when one hole of a pNet is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
filled by the same pNet, in other words, composing a pNet with two
bisimilar contexts. The general case will be obtained by
transitivity of the bisimulation relation.

@@

Intuition: tau is non observable if the automaton allows any tau transition from holes, and the global transition resulting from a tau in a hole is a tau transition not changing the action state.
\TODO{Id(s) is the identity function on variables of state s}
\begin{definition}[Non-observability of silent actions]
An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have
\begin{enumerate}
\item
\[ \openrule
         {
           (j\mapsto\tau),\symb{True},\symb{Id}(s)}
         {s \OTarrow {\tau} s}
         \in \mathcal{T}
\]
and 
\item for all $\alpha$, $j$, $s$, $\Post$ and $s'$ such that
\[ \openrule
         {
           (j\mapsto\tau),\Pred,\Post}
         {s \OTarrow {\alpha} s'}
         \in \mathcal{T} \] we have \[ \alpha=\tau\land s=s'\land \Post=\symb{Id}(s)
\]
\end{enumerate}
\end{definition}

@@

%\noindent{\bf Invisible $\tau$ transitions:}
\begin{mathpar}
 \openrule
         {
           \emptyset,\symb{True},Id(s)}
         {s \OTWeakarrow {\tau} s} \in \WT
 \end{mathpar}
and
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
}
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
%\inferrule{
% \openrule
%         {
%           \overline{\beta},\Pred,\Post}
%         {s \OTarrow {\tau} s'} \in \mathcal{T}
%\\
% \openrule
%         {
%           \overline{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
%         {s' \OTWeakarrow {\tau} s''} \in \WT
%}
%{ \openrule
%         {
%           \vis{\overline{\beta}}\dotcup\overline{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
%				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
%         {s \OTWeakarrow {\tau} s''} \in \WT
%}
 \end{mathpar}
and
%\noindent{\bf Other transitions:}
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in \WT
\qquad
\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
\qquad
\openrule
         {
           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s_2 \OTWeakarrow {\tau} s'} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
           \overline{\gamma_1}\dotcup \overline{\gamma_2}\dotcup\overline{\gamma_3},
		\Pred,
				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}

@@

Two pNets are Weak FH-bisimilar if there exist a relation between their associated 
automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
the predicate associated to the relation between the initial states is true.
 \end{definition}

@@

\subsection{Weak bisimulation for open pNets}
\begin{definition}[Non-observability of silent actions for pNets]~\\
A pNet $\mylangle \pNet_i^{i\in I} , \Sort_j^{j\in J}, \overline{\symb{SV}}\myrangle$
 \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\symb{True}}\in \overline{\symb{SV}}$ and $\forall SV_k\in \overline{\symb{SV}}, \forall i,j\in I_k\uplus J_k.\,i\neq j \Rightarrow \alpha'_k\neq\tau$
\end{definition}

@@

\noindent
     $  \openrule{
      \emptyset; Pred=true; Post=\{m_1\_m:=s_1\_m, m_1\_b:=s_1\_sb, s_2\_sb:=s_1\_sb\}
                      }
    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(s_1\_m, s_1\_b)}} \ostate{s_2,m_1,m_0,r_0}}
    $

@@

\medskip\noindent
     $  \openrule{
  \emptyset; Pred=true; Post=r_2\_b:=r_1\_b; s_2\_b:=s_1\_b   \}
                      }
    {\ostate{s_2,m_0,m_0,r_1} \OTarrow{out(r_1\_m)} \ostate{s_2,m_0,m_0,r_2}}
    $
    \\

@@

Where $j_0\in I_1$ or $j_0\in I_2$
We know each premise is true for $P[Q]_{j_0}$ and try to prove the equivalent premise for 
$P$. 
First, $K$ and the synchronisation vector $SV_k$ are unchanged\footnotemark (however 
$j_0$ passes from 
the set of subnets to the set of holes). 
%Then $SV=clone(\alpha_j^{j\in I_k\uplus\{j_0\}\uplus J_k})$.
We have $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$.

@@

       Consider each premise of the open transition (constructed by \TrDeux\ in 
Definition~\ref{def:operationalSemantics}). 
We know each premise is true for $P$ and try to prove the equivalent premise for 
$P[Q]_{j_0}$ (using the open transition of $Q$). 
$K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
$SV_k=\SV{(\alpha'_j)^{j\in I\uplus\{j_0\}\uplus 
	J}}{\alpha'}{e_b}$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. $I$ and $J$ 
	are the 
    set of leaves and holes of $P$, $I_1\uplus I_2$ and $J'$ are the sets of moving 
    leaves and holes 
    in the reduction of $P$. All sub-pNets of 
    must
    be 
reduced, we need:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
%variables}:
\[
    	\forall m\!\!\in\!\! I_1\uplus\{j_0\}. {\pNet_m 
    	\models\openrule
    	{
    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \]\[
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\openrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {\alpha_m}
    		\ostate{s_m'}} }\]
%\forall m\!\!\in\!\! I\cup \{j_0\}. 	
%    {\left(\begin{array}{l}
%	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
%    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
%    	\{\xrightarrow{\beta_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
%    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
%		{ \pNet_m 
%    	 \models
%    	\inferrule*[myfraction=\reddottedrule]
%    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
%    	{\ostate{s_m} \OTarrow {v_m}
%    		\ostate{s_m'}} \land I_m=\{m\} \land J_m=\emptyset}
%\end{array}\right)}\]
the sub-pNet at position $j_0$ is the one filled by $Q$ which offers an open transition 
by hypothesis, the other open transitions are immediate consequence of the open 
transition that can be performed by $P$ (premises of \TrDeux).
The set of moving leaves is the union of the moving leaves in the open transition for $P$ 
and the ones for $Q$: 
$I'_{PQ}= I'_P \uplus I'_Q$, similarly the moving holes are the union of the moving 
holes, minus $j_0$: $J'_{PQ}=  J\setminus\{j_0\}\uplus J_Q$. The 
predicate for the open 
transition is: $\Pred\,''=\bigwedge_{m\in I _1\uplus I_2}\Pred_m \land \Pred\,'
\land \Pred(SV_k,v_i^{i\in I_1\uplus I_2}\uplus(j_0\mapsto v_Q),\beta_j^{j\in 
J},\alpha)$. 
By definition 
$\Pred(SV_k,\alpha_i^{i\in I}\uplus(j_0\mapsto \alpha_Q),\beta_j^{j\in 
J},v)\Leftrightarrow
	\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\alpha'_j \land 
	\alpha=\alpha'\land \alpha_Q=\alpha_{j_0}\land e_b$,
this is equivalent to $\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, 
\beta_j=\alpha'_j \land 
	\alpha=\alpha'\land \alpha_Q=\beta_{j_0}\land \beta_{j_0}=\alpha_{j_0}\land e_b$
 and by definition of $\Pred$ (as obtained by \TrDeux),
	$\Pred\,''\iff \Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$. The post-condition 
	gathers the post-conditions related to all 
	the leaves. Finally, the composed open transition can be
        built. \qed
        \end{proof}
\end{small}

@@

By recurrence hypothesis the theorem is true for any set of transitions of length $l$. In particular, we have

@@

By rule (1) we have
${ \openrule
         {
          \emptyset,True,Id(s')
				 } {s' \OTWeakarrow {\tau} s'} \in \WT
}$
Finally by using rule (3) we compose the three rules:

@@

\begin{itemize}
\item case rule (WT1):
\begin{mathpar}
{ \openrule
         {
           \emptyset,\symb{True},\symb{Id}(s)
				 } {s \OTarrow {\tau} s} \in \mathcal{T}
}
\end{mathpar}
In this case we can directly conclude by the right part of the disjunction.

@@

%
%
%Basis: suppose that $\OTWeakarrow {\alpha}$ cannot be subdivided. So for a given weak transition:
%
%\begin{mathpar}
%{ \openrule
%         {
%           \overline{\gamma}\!,\Pred,\Post
%				 } {s \OTWeakarrow {\alpha} s'} \in \WT
%}
%\end{mathpar}
%We have two cases:
%\begin{itemize}
\item either $\alpha = \tau$, $s=s'$, $\overline{\beta}=\emptyset$, $\Pred = \symb{True}$ and $\Post=\symb{Id}(s)$. So by rule (2) we have:

@@

\begin{mathpar}
  \inferrule
      {\inferrule*
        {0 \xrightarrow{ium(?tgt2_2), True, \emptyset}_{gw2} 2}
        {\sm{gw2} \models
             \openrule {0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2}
                       {\ostate{0} \xrightarrow{ium(?tgt2_2)} \ostate{2} }
             }
        \quad
        \inferrule* [right={[UM\_21]}]
           {
             %\sm{fresh}(b_{P21},v_{SG2})
           }
           {\sm{SG2} \models
             \openrule {\xrightarrow{b}_{P21} \quad \sm{Pred}_{UM\_21}}
                       {\ostate{-} \xrightarrow{v_{SG2}} \ostate{-} }
             }
%           \\ {\sm{fresh}(t1,t2,v) }
           \quad
           \sm{Pred}_{UG\_2}
      }
      {p\_Root
     \models
     \openrule
         {0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2 \\
           \xrightarrow{b}_{P21}
          \\ \sm{Pred1}}
         {\ostate{000} \OTarrow{v} \ostate{020}}
      }      ~~ [UG\_2]
\end{mathpar}
With:

@@

\begin{mathpar}
  \inferrule
      {\inferrule
        {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1}
        { \sm{gw1} \models
          \openrule
              {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad \sm{True}}
              {\ostate{0} \OTarrow{im(?tgt1_1)} \ostate{1}}
        }
        \\
       \inferrule
           {2 \xrightarrow{bm(tgt2_2)}_{gw2} 0}
           { \sm{gw2} \models
             \openrule
                 {2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad \sm{Pred}_{gw2}}
                 {\ostate{2} \OTarrow{bm(tgt2_2)} \ostate{0}}
           }
           \quad Pred_{HB\_2}
      }
           {p\_Root
     \models
     \openrule
         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
           \xrightarrow{b}_{P3}
           \quad Pred2}
         {\ostate{020} \OTarrow{v} \ostate{100}}}
      ~~ [HB\_2]
\end{mathpar}

@@

\begin{mathpar}
    \inferrule{\phi,\phi',\phi''\!\in\!\Phi\\s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle} s'\in \to\\\\
      \phi'\!=\!\phi\!+\!\{x'_i\!\to\!V_i|x'_i\!\in\!\iv(\alpha)\land V_i\!\in\!\mathcal{D}\} \\
      e_b\phi'\!=\!\symb{True} \\ \phi''\!=\!\phi'+\{x_j\!\to\! e_j\phi'|j\!\in\! J\}}
    {(s,\phi) \xrightarrow{\alpha\phi'} (s',\phi'') \in\llbracket\mylangle S,s_0,
      \to\myrangle\rrbracket_\Phi}~~{\TrUn}
%         \end{mathpar}
% \begin{mathpar}

>>>>

Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
$\mathcal{S}_2$ constrained by a predicate
More precisely, for any pair $(s,t)$, there is a 
   single
      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
      if $\Pred_{s,t}$       is 
      t\\True, i.e. the states are related when the variables in $s$ and $t$ verify the 
      predicate $\Pred_{s,t}$.
 FH-bisimulation is defined formally: 
 \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}

@@

     $  OT_2  = \openrule{
      \emptyset; Pred=\True;  \\ Post=\{m_1\_m:=s_1\_m, m_1\_b:=s_1\_sb, s_2\_sb:=s_1\_sb\}
                      }
    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(s_1\_m, s_1\_b)}} \ostate{s_2,m_1,m_0,r_0}}
    $

@@

\subsection{Bisimulation for open pNets and Composability}
\label{section:bisimulation-PN}
As  our symbolic operational semantics provides an open automaton, we can apply the notion of
	strong (symbolic) bisimulation on automata to open pNet s:
\begin{definition}[FH-bisimulation for open pNets]\label{def:bisim-pnets}
Two pNets are FH-bisimilar if there exist a relation between their associated 
automata that is an FH-bisimulation and their initial states are in the relation, i.e. 
the predicate associated to the relation between the initial states is \True.
\end{definition}
We can now prove that pNet composition  preserves
FH-bisimulation. More precisely, one can define two preservation
properties, namely 1) when one hole of a pNet is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
filled by the same pNet, in other words, composing a pNet with two
bisimilar contexts. The general case will be obtained by
transitivity of the bisimulation relation.

@@

Intuition: tau is non observable if the automaton allows any tau transition from holes, and the global transition resulting from a tau in a hole is a tau transition not changing the action state.
\TODO{Id(s) is the identity function on variables of state s}
\begin{definition}[Non-observability of silent actions]
An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have
\begin{enumerate}
\item
\[ \openrule
         {
           (j\mapsto\tau),\True,\Id(s)}
         {s \OTarrow {\tau} s}
         \in \mathcal{T}
\]
and 
\item for all $\alpha$, $j$, $s$, $\Post$ and $s'$ such that
\[ \openrule
         {
           (j\mapsto\tau),\Pred,\Post}
         {s \OTarrow {\alpha} s'}
         \in \mathcal{T} \] we have \[ \alpha=\tau\land s=s'\land \Post=\Id(s)
\]
\end{enumerate}
\end{definition}

@@

%\noindent{\bf Invisible $\tau$ transitions:}
\begin{mathpar}
 \openrule
         {
           \emptyset,\True,\Id(s)}
         {s \OTWeakarrow {\tau} s} \in \WT
 \end{mathpar}
and
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule{
 \openrule
         {
           \overline{\beta},\Pred,\Post}
         {s \OTarrow {\alpha} s'} \in \mathcal{T}
}
{ \openrule
         {
           \vis{\overline{\beta}}\!,\Pred,\Post
				 } {s \OTWeakarrow {\alpha} s'} \in \WT
}
%\inferrule{
% \openrule
%         {
%           \overline{\beta},\Pred,\Post}
%         {s \OTarrow {\tau} s'} \in \mathcal{T}
%\\
% \openrule
%         {
%           \overline{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
%         {s' \OTWeakarrow {\tau} s''} \in \WT
%}
%{ \openrule
%         {
%           \vis{\overline{\beta}}\dotcup\overline{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
%				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
%         {s \OTWeakarrow {\tau} s''} \in \WT
%}
 \end{mathpar}
and
%\noindent{\bf Other transitions:}
\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \overline{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in \WT
\qquad
\openrule
         {
           \overline{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
\qquad
\openrule
         {
           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s_2 \OTWeakarrow {\tau} s'} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
           \overline{\gamma_1}\dotcup \overline{\gamma_2}\dotcup\overline{\gamma_3},
		\Pred,
				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s'} \in\WT
}
\end{mathpar}

@@

Two pNets are Weak FH-bisimilar if there exist a relation between their associated 
automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
the predicate associated to the relation between the initial states is \True.
 \end{definition}

@@

\subsection{Weak bisimulation for open pNets}
\begin{definition}[Non-observability of silent actions for pNets]~\\
A pNet $\mylangle \pNet_i^{i\in I} , \Sort_j^{j\in J}, \overline{\symb{SV}}\myrangle$
 \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\True}\in \overline{\symb{SV}}$ and $\forall SV_k\in \overline{\symb{SV}}, \forall i,j\in I_k\uplus J_k.\,i\neq j \Rightarrow \alpha'_k\neq\tau$
\end{definition}

@@

\noindent
     $  \openrule{
      \emptyset; Pred=\True; Post=\{m_1\_m:=s_1\_m, m_1\_b:=s_1\_sb, s_2\_sb:=s_1\_sb\}
                      }
    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(s_1\_m, s_1\_b)}} \ostate{s_2,m_1,m_0,r_0}}
    $

@@

\medskip\noindent
     $  \openrule{
  \emptyset; Pred=\True; Post=r_2\_b:=r_1\_b; s_2\_b:=s_1\_b   \}
                      }
    {\ostate{s_2,m_0,m_0,r_1} \OTarrow{out(r_1\_m)} \ostate{s_2,m_0,m_0,r_2}}
    $
    \\

@@

Where $j_0\in I_1$ or $j_0\in I_2$
We know each premise is \True for $P[Q]_{j_0}$ and try to prove the equivalent premise for 
$P$. 
First, $K$ and the synchronisation vector $SV_k$ are unchanged\footnotemark (however 
$j_0$ passes from 
the set of subnets to the set of holes). 
%Then $SV=clone(\alpha_j^{j\in I_k\uplus\{j_0\}\uplus J_k})$.
We have $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$.

@@

       Consider each premise of the open transition (constructed by \TrDeux\ in 
Definition~\ref{def:operationalSemantics}). 
We know each premise is \True for $P$ and try to prove the equivalent premise for 
$P[Q]_{j_0}$ (using the open transition of $Q$). 
$K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
$SV_k=\SV{(\alpha'_j)^{j\in I\uplus\{j_0\}\uplus 
	J}}{\alpha'}{e_b}$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. $I$ and $J$ 
	are the 
    set of leaves and holes of $P$, $I_1\uplus I_2$ and $J'$ are the sets of moving 
    leaves and holes 
    in the reduction of $P$. All sub-pNets of 
    must
    be 
reduced, we need:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
%variables}:
\[
    	\forall m\!\!\in\!\! I_1\uplus\{j_0\}. {\pNet_m 
    	\models\openrule
    	{
    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
  \]\[
\forall m\!\!\in\!\! I_2.		{ \pNet_m 
    	 \models
    	\openrule
    	{\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {\alpha_m}
    		\ostate{s_m'}} }\]
%\forall m\!\!\in\!\! I\cup \{j_0\}. 	
%    {\left(\begin{array}{l}
%	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
%    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
%    	\{\xrightarrow{\beta_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
%    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
%		{ \pNet_m 
%    	 \models
%    	\inferrule*[myfraction=\reddottedrule]
%    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
%    	{\ostate{s_m} \OTarrow {v_m}
%    		\ostate{s_m'}} \land I_m=\{m\} \land J_m=\emptyset}
%\end{array}\right)}\]
the sub-pNet at position $j_0$ is the one filled by $Q$ which offers an open transition 
by hypothesis, the other open transitions are immediate consequence of the open 
transition that can be performed by $P$ (premises of \TrDeux).
The set of moving leaves is the union of the moving leaves in the open transition for $P$ 
and the ones for $Q$: 
$I'_{PQ}= I'_P \uplus I'_Q$, similarly the moving holes are the union of the moving 
holes, minus $j_0$: $J'_{PQ}=  J\setminus\{j_0\}\uplus J_Q$. The 
predicate for the open 
transition is: $\Pred\,''=\bigwedge_{m\in I _1\uplus I_2}\Pred_m \land \Pred\,'
\land \Pred(SV_k,v_i^{i\in I_1\uplus I_2}\uplus(j_0\mapsto v_Q),\beta_j^{j\in 
J},\alpha)$. 
By definition 
$\Pred(SV_k,\alpha_i^{i\in I}\uplus(j_0\mapsto \alpha_Q),\beta_j^{j\in 
J},v)\Leftrightarrow
	\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\alpha'_j \land 
	\alpha=\alpha'\land \alpha_Q=\alpha_{j_0}\land e_b$,
this is equivalent to $\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, 
\beta_j=\alpha'_j \land 
	\alpha=\alpha'\land \alpha_Q=\beta_{j_0}\land \beta_{j_0}=\alpha_{j_0}\land e_b$
 and by definition of $\Pred$ (as obtained by \TrDeux),
	$\Pred\,''\iff \Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$. The post-condition 
	gathers the post-conditions related to all 
	the leaves. Finally, the composed open transition can be
        built. \qed
        \end{proof}
\end{small}

@@

By recurrence hypothesis the theorem is \True for any set of transitions of length $l$. In particular, we have

@@

By rule (1) we have
${ \openrule
         {
          \emptyset,\True,\Id(s')
				 } {s' \OTWeakarrow {\tau} s'} \in \WT
}$
Finally by using rule (3) we compose the three rules:

@@

\begin{itemize}
\item case rule (WT1):
\begin{mathpar}
{ \openrule
         {
           \emptyset,\True,\Id(s)
				 } {s \OTarrow {\tau} s} \in \mathcal{T}
}
\end{mathpar}
In this case we can directly conclude by the right part of the disjunction.

@@

%
%
%Basis: suppose that $\OTWeakarrow {\alpha}$ cannot be subdivided. So for a given weak transition:
%
%\begin{mathpar}
%{ \openrule
%         {
%           \overline{\gamma}\!,\Pred,\Post
%				 } {s \OTWeakarrow {\alpha} s'} \in \WT
%}
%\end{mathpar}
%We have two cases:
%\begin{itemize}
\item either $\alpha = \tau$, $s=s'$, $\overline{\beta}=\emptyset$, $\Pred = \True$ and $\Post=\Id(s)$. So by rule (2) we have:

@@

\begin{mathpar}
  \inferrule
      {\inferrule*
        {0 \xrightarrow{ium(?tgt2_2), \True, \emptyset}_{gw2} 2}
        {\sm{gw2} \models
             \openrule {0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2}
                       {\ostate{0} \xrightarrow{ium(?tgt2_2)} \ostate{2} }
             }
        \quad
        \inferrule* [right={[UM\_21]}]
           {
             %\sm{fresh}(b_{P21},v_{SG2})
           }
           {\sm{SG2} \models
             \openrule {\xrightarrow{b}_{P21} \quad \sm{Pred}_{UM\_21}}
                       {\ostate{-} \xrightarrow{v_{SG2}} \ostate{-} }
             }
%           \\ {\sm{fresh}(t1,t2,v) }
           \quad
           \sm{Pred}_{UG\_2}
      }
      {p\_Root
     \models
     \openrule
         {0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2 \\
           \xrightarrow{b}_{P21}
          \\ \sm{Pred1}}
         {\ostate{000} \OTarrow{v} \ostate{020}}
      }      ~~ [UG\_2]
\end{mathpar}
With:

@@

\begin{mathpar}
  \inferrule
      {\inferrule
        {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1}
        { \sm{gw1} \models
          \openrule
              {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad \True}
              {\ostate{0} \OTarrow{im(?tgt1_1)} \ostate{1}}
        }
        \\
       \inferrule
           {2 \xrightarrow{bm(tgt2_2)}_{gw2} 0}
           { \sm{gw2} \models
             \openrule
                 {2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad \sm{Pred}_{gw2}}
                 {\ostate{2} \OTarrow{bm(tgt2_2)} \ostate{0}}
           }
           \quad Pred_{HB\_2}
      }
           {p\_Root
     \models
     \openrule
         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
           \xrightarrow{b}_{P3}
           \quad Pred2}
         {\ostate{020} \OTarrow{v} \ostate{100}}}
      ~~ [HB\_2]
\end{mathpar}

@@

\begin{mathpar}
    \inferrule{\phi,\phi',\phi''\!\in\!\Phi\\s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle} s'\in \to\\\\
      \phi'\!=\!\phi\!+\!\{x'_i\!\to\!V_i|x'_i\!\in\!\iv(\alpha)\land V_i\!\in\!\mathcal{D}\} \\
      e_b\phi'\!=\!\True \\ \phi''\!=\!\phi'+\{x_j\!\to\! e_j\phi'|j\!\in\! J\}}
    {(s,\phi) \xrightarrow{\alpha\phi'} (s',\phi'') \in\llbracket\mylangle S,s_0,
      \to\myrangle\rrbracket_\Phi}~~{\TrUn}
%         \end{mathpar}
% \begin{mathpar}
